---
title: "Homework 04 - Data Classes w. forcats & lubridate"
author: "Vincent Baker"
date: "3/9/23"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro) 
library(lubridate)
library(glue)
```

## Exercises

### Exercise 1

```{r my-vectors}
numeric <- c(2, 4, 6, 8, 10)

character <- c("Seconds", "Minutes", "Hours", "Days", "Weeks")

mixed <- c(2, "Minutes", 6, "Hours", 10)
```

"numeric" is a `r typeof(numeric)` data type, "character" is a `r typeof(character)` data type, and "mixed" is a `r typeof(mixed)` data type.

"numeric" is a `r class(numeric)` vector, "character" is a `r class(character)` vector, and "mixed" is a `r class(mixed)` vector.

### Exercise 2

```{r data-frame , eval = T}
data_frame <- bind_cols("numeric" = numeric, "character" = character, "mixed" = mixed)
data_frame
```

This data frame is a `r typeof(data_frame)` and is a `r class(data_frame)`. 

### Exercise 3

```{r my-vectors-2, eval = T}
numeric <- c(5,10,15,20,25)

character <- c("Mammals", "Reptiles", "Amphibians", "Fish")

mixed <- c(5, "Mammals", 10, "Reptiles", 15)

#data_frame_2 <- bind_cols("numeric" = numeric, "character" = character, "mixed" = mixed)
#data_frame_2
```

This code chunk will not run because vector "character" has only 4 components while the other two have 5 and all vectors need to have the same amount of components.

### Exercise 4

```{r data-frame-2, eval = T}
data_frame_2 <- list("numeric" = numeric, "character" = character, "mixed" = mixed)
data_frame_2
```

The list() function basically creates vectors into a list of the components and works well with this data frame because r isn't checking for the length of the vectors. 

### Exercise 5

```{r earthquakes-factors}
earthquakes %>% 
  ggplot(aes(x = month)) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
typeof(month)
```

1) month is characterized as a closure (function) data type instead of a character data type.
2) The months are out of order because r is placing the months in alphabetical order.

### Exercise 6

```{r earthquakes-forcats-1}
earthquakes %>% 
  ggplot(aes(x = fct_infreq(month))) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```

The fct_infreq() function is reordering the the months in descending order of the amount of earthquakes occurring within each month. The months are still out of order, but at least the data is more understandable.  

```{r earthquakes-forcats-2}
earthquakes %>% 
  ggplot(aes(x = fct_rev(month))) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```

The fct_rev() function is reversing the order of the months from the first graph which listed the months in alphabetical order.  

```{r earthquakes-forcats-3}
earthquakes %>% 
  ggplot(aes(x = fct_inorder(month))) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```

The fct_inorder() function orders the months in the order of when the data was collected; April is the first month when the data was collected.  

```{r earthquakes-forcats-4}
earthquakes %>% 
  ggplot(aes(x = month %>% fct_infreq() %>% fct_rev())) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```

By combing the fct_infreq() and fct_rev() functions, it orders the months by the frequency of earthquakes and reverses the order from least to greatest.  

```{r earthquakes-forcats-5}
earthquakes %>% 
  mutate(month = fct_recode(month,
                            "1" = "January",
                            "2" = "February",
                            "3" = "March",
                            "4" = "April",
                            "5" = "May",
                            "6" = "June",
                            "7" = "July",
                            "8" = "August",
                            "9" = "September",
                            "10" = "October",
                            "11" = "November",
                            "12" = "December")) %>% 
  ggplot(aes(x = factor(as.numeric(month)))) +
  geom_bar() +
  labs(x = "Month of the year", y = "Earthquake count")
```

The fct_recode() function enables you to rename the factors or names; "months" are now numerical values, but is even more confusing because they do not necessarily correlate with the months; April is listed as "1." 

### Exercise 7

```{r earthquake-dates}
earthquakes_new <- earthquakes %>% 
  mutate(date = glue("{year} {month} {day}")) %>% 
  relocate(date)
print(earthquakes_new)
```

mutate() allows you to keep existing variables and add new ones; "date" combines year, month, and day, and creates a new variable. relocate() allows you to change the column positions in a data set; "date" is before year.
date is a `r typeof(date)` data type and is a `r class(date)` vector. 

### Exercise 8

```{r earthquakes-new}
earthquakes_new %>%
  filter(year == 1933) %>%
  ggplot(aes(x = date, y = richter)) +
  geom_point()
```

This scatter plot only shows earthquakes that occurred in 1933  because that was the only year that was selected. 

### Exercise 9

```{r earthquakes-dates2, eval = F}
earthquakes %>% 
  mutate(date = ___(glue("{year} {month} {day}"))) %>% 
  relocate(date) %>% 
  ggplot(aes(x = date, y = richter)) +
  geom_point() 
```



