---
title: "Homework 04 - Data Classes w. forcats & lubridate"
author: "Vincent Baker"
date: "3/9/23"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro) 
library(lubridate)
```

## Exercises

### Exercise 1

```{r my-vectors}
numeric <- c(2, 4, 6, 8, 10)

character <- c("Seconds", "Minutes", "Hours", "Days", "Weeks")

mixed <- c(2, "Minutes", 6, "Hours", 10)
```

"numeric" is a `r typeof(numeric)` data type, "character" is a `r typeof(character)` data type, and "mixed" is a `r typeof(mixed)` data type.

"numeric" is a `r class(numeric)`vector, "character" is a `r class(character)` vector, and "mixed" is a `r class(mixed)` vector.

### Exercise 2

```{r data-frame , eval = T}
data_frame <- bind_cols("numeric" = numeric, "character" = character, "mixed" = mixed)
data_frame
```

This data frame is a `r typeof(data_frame)` and is a `r class(data_frame)`. 

### Exercise 3

```{r data-frame-2, eval = F}
numeric <- c(5,10,15,20,25)

character <- c("Mammals", "Reptiles", "Amphibians", "Fish")

mixed <- c(5, "Mammals", 10, "Reptiles", 15)

data_frame_2 <- bind_cols("numeric" = numeric, "character" = character, "mixed" = mixed)
data_frame_2
```

This code chunk will not run because vector "character" has only 4 components while the other two have 5 and all vectors need to have the same amount of components.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 10 here.
