---
title: "Lab 04 - Data Type Coercion"
author: "Vincent Baker"
date: "3/7/23"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(openintro)
```

## Exercises

### Exercise 1

```{r echo = F}
1
1L
"C"
```

1 is a type double.
1L is a type integer.
C is a type character. 

```{r echo = F}
c(1, 1L, "C")
```

The second code chunk gives the output as a vector. 

```{r echo = F}
typeof(c(1, 1L, "C"))
```

All of the components in the vector have to be the same; since "C" is a character and it cannot be a numerical, the others have to default to a type character as well. 

### Exercise 2


Remove this text, and add your answer for Exercise 2 here.

### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 9 here.
