---
title: "Lab 04 - Data Type Coercion"
author: "Vincent Baker"
date: "3/7/23"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(openintro)
```

## Exercises

### Exercise 1

```{r echo = F}
1
1L
"C"
```

1 is a `r typeof(1)`, 1L is an `r typeof(1L)`, and C is `r typeof("C")`.

```{r echo = F}
c(1, 1L, "C")
```

The second code chunk gives the output as a vector. 

```{r echo = F}
typeof(c(1, 1L, "C"))
```

All of the components in the vector have to be the same; since "C" is a character and it cannot be a numerical, the others have to default to a type character as well. 

### Exercise 2

```{r echo = F}
1:3
5
```

The data type for 1:3 is `r typeof(1:3)` and the data type for 5 is `r typeof(5)`.

```{r echo = F}
typeof(c(1:3, 5))
```

The vector is a type double because "1:3" is defaulted to a type double because type doubles such as "5" trump integers.

### Exercise 3

```{r echo = F}
3 
FALSE
T
```

3 is a `r typeof(3)`, FALSE is `r typeof(FALSE)`, and TRUE is `r typeof(TRUE)`.

```{r echo = F}
typeof(c(3, FALSE, T))
```

The vector is considered a double data type because FALSE and T (TRUE) are logical and type double is the immediate default.

### Exercise 4

```{r echo = F}
TRUE
as.numeric(TRUE)
```

TRUE is `r typeof(TRUE)` and 1 is a `r typeof(1)`.

```{r echo = F}
typeof(c(TRUE, as.numeric(TRUE)))
```

The output shows this vector is a double data type because as.numeric() changes TRUE into a double and the vector defaults to a double data type.   

### Exercise 5

```{r echo = F}
NA
FALSE
as.logical(1)
```

Na is `r typeof(NA)`, FALSE is `r typeof(FALSE)`, and TRUE is `r typeof(TRUE)`.

```{r echo = F}
typeof(c(NA, FALSE, as.logical(1)))
```

This vector is a logical data type because as.logical() converts "1" into a logical data type and now all three components are logical data types. Without as.logical(), "1" would be considered a double data type, and the whole vector would be a double.  

### Exercise 6

```{r echo = F}
1L
0
1L / 0
"A"
```

1L is `r typeof(1L)`, 0 is `r typeof(0)`, in 1L / 0, 1L is `r typeof(1L)`, 0 is `r typeof(0)`, and together is a `r typeof(1L / 0)`, and A is a `r typeof("A")`. 

```{r echo = F}
typeof(c(1L / 0, "A"))
```

This vector is a character data type because even though 1L / 0 is a double, the vector was default to a character data type because of "A."

### Exercise 7

```{r earthquakes}
glimpse(earthquakes)
```

### Exercise 8



### Exercise 9

Remove this text, and add your answer for Exercise 9 here.

### Exercise 10

Remove this text, and add your answer for Exercise 9 here.
